---
title: "2021_MARSSModel_Klamath"
output:
  word_document: default
  html_document: default
---

---
title: "2021_MARSSModel"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(patchwork)
library(astsa)
library(forecast)
library(dplyr)
library(pander)
library(MARSS)
library(MASS)
library(gridExtra)
library(weathermetrics)
```

##Read in data
```{r echo = T, results = "hide", messages = F}
KSV_meantemps <- readRDS('KSV_meantemps.rds')
daily_means_long_klamath <- readRDS('daily_means_long.rds')
covariate_klamath <- readRDS('covariate.rds')

daily_means_long_klamath <-rbind(daily_means_long_klamath, KSV = KSV_meantemps)
str(daily_means_long_klamath)

```


##Data Matrix 
```{r echo = T, results = "hide", messages = F}
#Convert data to matrix 
daily_means_long_klamath <- as.matrix(daily_means_long_klamath)
saveRDS(daily_means_long_klamath,"daily_means_long_klamath.rds")

#z score
transformed_dat_klamath <- as.matrix(daily_means_long_klamath)
transformed_dat_klamath <- zscore(transformed_dat_klamath)
saveRDS(transformed_dat_klamath,"transformed_dat_klamath.rds")

```

##Covariates
```{r echo = T, results = "hide", messages = F}
#Build the little c matrix, call it matrixc
matrixc_klamath <- matrix(nrow=1,ncol=378)
matrixc_klamath <- (as.matrix(covariate_klamath))
saveRDS(matrixc_klamath,"matrixc_klamath.rds")

```

###Check data and covariates
```{r}
matplot(t(transformed_dat_klamath))
matplot(t(matrixc_klamath))

#looks okay, we removed AP2 in the visualization .rmd file
```

##Z-Matrices
###matrix2_klamath
```{r echo = T}
#Hypothesis 1: All ponds and creeks and mainstem are separate
matrix2_klamath <- matrix(nrow=26,ncol=12)
matrix2_klamath[c(1:2),1] <- 1 #Alexander
matrix2_klamath[c(1:2),c(2:12)] <- 0
matrix2_klamath[c(4:5),2] <- 1 #Stender
matrix2_klamath[c(4:5),c(1,3:12)] <- 0 
matrix2_klamath[c(3,6,9,11,12),3] <- 1 #Seiad Creek
matrix2_klamath[c(3,6,9,11,12),c(1,2,4:12)] <- 0
matrix2_klamath[7,4] <- 1 #Durazo
matrix2_klamath[7,c(1:3,5:12)] <- 0
matrix2_klamath[8,5] <- 1 #Lower Seiad
matrix2_klamath[8,c(1:4,6:12)] <- 0
matrix2_klamath[10,6] <- 1 #May
matrix2_klamath[10,c(1:5,7:12)] <- 0
matrix2_klamath[c(12:13),7] <- 1 #Fish Gulch
matrix2_klamath[c(12:13),c(1:6,8:12)] <- 0
matrix2_klamath[c(15:17),8] <- 1 #Goodman
matrix2_klamath[c(15:17),c(1:7,9:12)] <- 0
matrix2_klamath[c(19:21),9] <- 1 #Upper Lawrence
matrix2_klamath[c(19:21),c(1:8,10:12)] <- 0
matrix2_klamath[c(23:25),10] <- 1 #Lower Lawrence
matrix2_klamath[c(23:25),c(1:9,11:12)] <- 0
matrix2_klamath[c(14,18,22),11] <- 1 #Horse Creek
matrix2_klamath[c(14,18,22),c(1:10,12)] <- 0
matrix2_klamath[26,12] <- 1 #Klamath
matrix2_klamath[26,c(1:11)] <- 0
matrix2_klamath
```

###matrix3_klamath
```{r echo = T}
#Hypothesis 2: ponds versus creeks versus Klamath
matrix3_klamath <- matrix(nrow=26, ncol=3)
matrix3_klamath[c(1:2,4:5,7:8,10,12:13,15:17,19:21,23:25),1] <- 1 #All ponds
matrix3_klamath[c(1:2,4:5,7:8,10,12:13,15:17,19:21,23:25),c(2:3)] <- 0
matrix3_klamath[c(3,6,9,11,14,18,22),c(1,3)] <- 0 #All creeks
matrix3_klamath[c(3,6,9,11,14,18,22),2] <- 1
matrix3_klamath[26,3] <- 1 #Klamath
matrix3_klamath[26,c(1:2)] <- 0 
matrix3_klamath
```

###matrix4_klamath
```{r echo = T}
#Hypothesis 3: tributary versus tributary versus Klamath
matrix4_klamath <-matrix(nrow=26,ncol=5)
matrix4_klamath[c(1:2,4:5,7:8,10),1] <- 1  #Seiad Creek Ponds
matrix4_klamath[c(1:2,4:5,7:8,10),c(2:5)] <- 0
matrix4_klamath[c(3,6,9,11),2] <- 1 #Seiad Creek
matrix4_klamath[c(3,6,9,11),c(1,3:5)] <- 0
matrix4_klamath[c(12:13,15:17,19:21,23:25),3] <- 1 #Horse Creek Ponds
matrix4_klamath[c(12:13,15:17,19:21,23:25),c(1,2,4,5)] <- 0
matrix4_klamath[c(14,18,22),4] <- 1 #Horse Creek
matrix4_klamath[c(14,18,22),c(1:3,5)] <- 0
matrix4_klamath[26,5] <- 1 #Klamath
matrix4_klamath[c(26),c(1:4)] <- 0
matrix4_klamath
```

###matrix5_klamath
```{r echo = T}
#Hypothesis 4: All sensors are the same
matrix5_klamath <-  matrix(nrow=26, ncol=1)
matrix5_klamath[,] <- 1
matrix5_klamath

saveRDS(matrix2_klamath,"matrix2_klamath.rds")
saveRDS(matrix3_klamath,"matrix3_klamath.rds")
saveRDS(matrix4_klamath,"matrix4_klamath.rds")
saveRDS(matrix5_klamath,"matrix5_klamath.rds")
```

##MARSS models
###Create a FT for seasonality and combine with AirTemp
```{r}
#Correct for seasonality using Fourier Series
TT = ncol(transformed_dat_klamath) # number of time periods/samples
period = 365 # number of "seasons" (e.g., 12 months per year)
per.1st = 182 # first "season" (e.g., Jan = 1, July = 7)
c = diag(period) # create factors for seasons
for(i in 2:(ceiling(TT/period))) {c = cbind(c,diag(period))}
dim(c)

#Create Fourier Series
cos.t = cos(2 * pi * seq(TT) / period)
sin.t = sin(2 * pi * seq(TT) / period)
c.Four = rbind(cos.t,sin.t)
cor(c.Four[1,],c.Four[2,]) # not correlated!
matplot(t(c.Four), type="l")

#Now fit model with seasonality AND an additional covariate (airtemp from above)
matrixc_klamath_z <- zscore(matrixc_klamath)
newcovarsFour_airtemp <-rbind(c.Four, "airtemp"=matrixc_klamath_z)
matplot(t(newcovarsFour_airtemp), type="l", col=c("black","red","blue"))
```

####Things I tried: 1) zscore data + covar; 2) no zscore; 3) zscore covar; 4) zscore data; 5) no covar at all; 6) zscore covar + FT; 6) just FT

###model 1
```{r}
#Hypothesis 1, Model 1: all separate
mod11_klamath = list()
mod11_klamath$A = "zero" #no trend because we z scored
mod11_klamath$Z = matrix2_klamath
mod11_klamath$R = "diagonal and equal" #all the sensors are same, so observation error should be same
mod11_klamath$Q = "diagonal and unequal" 
mod11_klamath$B = "identity" #assuming no species interactions
mod11_klamath$U = "zero" #no trend because we z scored 
mod11_klamath$C = "unequal" #Can set C to unequal because it is going off the Z matrix where I have already indicated how to split up the sites.
mod11_klamath$c = matrixc_klamath
mod11_klamath.fit = MARSS(transformed_dat_klamath, model=mod11_klamath, control=list(maxit=10000))
mod11_klamath.params = MARSSparamCIs(mod11_klamath.fit)
saveRDS(mod11_klamath.fit,"mod11_klamath.fit.rds")
saveRDS(mod11_klamath.params,"mod11_klamath.params.rds")
```

####Messing with Residuals
```{r}
mod11_klamath.fit <- readRDS("mod11_klamath.fit.rds")
mod11_klamath.params <- readRDS("mod11_klamath.params.rds")

#model.residuals = the model residuals (data minus model predicted values) as a n x T matrix

#tT: smoothed residuals conditioned on all the data t=1 to T, aka smoothation residuals *Smoothed residuals are autocorrelated so an ACF test would not reveal model inadequacy
par(mfrow=c(4,2), mai=c(0.1,0.5,0.2,0.1),omi=c(0.5,0,0,0))
for (j in 1:12) {
  plot.ts(residuals<-MARSSresiduals(mod11_klamath.fit, type = "tT")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
}

#tt1: one-step-ahead residuals, aka innovations residuals
par(mfrow=c(4,2), mai=c(0.1,0.5,0.2,0.1),omi=c(0.5,0,0,0))
for (j in 1:12) {
  plot.ts(residuals<-MARSSresiduals(mod11_klamath.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
}

#tt: contemporaneous residuals, only for the observations
par(mfrow=c(4,2), mai=c(0.1,0.5,0.2,0.1),omi=c(0.5,0,0,0))
for (j in 1:12) {
  plot.ts(residuals<-MARSSresiduals(mod11_klamath.fit, type = "tt")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
}

```

###model 2
```{r}
#Hypothesis 2, Model 3: ponds vs. creeks 
mod12_klamath <- mod11_klamath 
mod12_klamath$Z <- matrix3_klamath
mod12_klamath$c <- matrixc_klamath
mod12_klamath.fit = MARSS(transformed_dat_klamath, model=mod12_klamath, control=list(maxit=10000))
mod12_klamath.params = MARSSparamCIs(mod12_klamath.fit)
saveRDS(mod12_klamath.fit,"mod12_klamath.fit.rds")
saveRDS(mod12_klamath.params,"mod12_klamath.params.rds")

par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:8) {
    plot.ts(residuals<-MARSSresiduals(mod12_klamath.fit, type = "tt")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

###model 3
```{r}
#Hypothesis 3, Model 3: Tributary versus tributary
mod13_klamath <- mod11_klamath
mod13_klamath$Z = matrix4_klamath
mod13_klamath.fit = MARSS(transformed_dat_klamath, model=mod13_klamath, control=list(maxit=10000))
mod13_klamath.params = MARSSparamCIs(mod13_klamath.fit)
saveRDS(mod13_klamath.fit,"mod13_klamath.fit.rds")
saveRDS(mod13_klamath.params,"mod13_klamath.params.rds")

par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod13_klamath.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

###model 4
```{r}
#Hypothesis 4, Model 4: All same
mod14_klamath <- mod11_klamath
mod14_klamath$Z <- matrix5_klamath
mod14_klamath.fit = MARSS(transformed_dat_klamath, model=mod14_klamath, control=list(maxit=10000))
mod14_klamath.params =MARSSparamCIs(mod14_klamath.fit)
saveRDS(mod14_klamath.fit,"mod14_klamath.fit.rds")
saveRDS(mod14_klamath.params,"mod14_klamath.params.rds")

par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod14_klamath.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

##AICc 
```{r}
data.frame(Model=c("Model11_klamath", "Model12_klamath", "Model13_klamath", "Model14_klamath"),
           AICc=round(c(mod11_klamath.fit$AICc,
                        mod12_klamath.fit$AICc,
                        mod13_klamath.fit$AICc,
                        mod14_klamath.fit$AICc),1))
```

