---
title: "2021_MARSSModel_Condense"
output:
  word_document: default
  html_document: default
---

```{r}
library(MARSS)
library(xtable)
library(tidyverse)
```

#Read in data 
```{r echo = T, results = "hide", messages = F}
#Matrix Klamath + pond dataset
daily_means_long_klamath <- readRDS('daily_means_long_klamath.rds')
transformed_dat_klamath <- readRDS('transformed_dat_klamath.rds')
transformed_dat_klamath_df <- as.data.frame(t(transformed_dat_klamath))
str(transformed_dat_klamath)

#Matrix Airtemp dataset
covariate_klamath <- readRDS('covariate.rds')
transformed_covariate_klamath <- zscore(covariate_klamath)
```
# Steps:
# 1) Among sensor replicates, drop time series with (many) gaps. 
# 2) Then take mean across replicate sensors, so that we end up with 1 time series per habitat, 2+9+1 (12 x 378)

```{r}
#AP
color <- c("AP1" = "blue", "AP3" = "red")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = AP1, color = "AP1")) +
  geom_line(aes(x = day, y = AP3, color = "AP3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("AP1","AP3"))
#need to remove AP1
```


```{r}
#SP
color <- c("SP1" = "blue", "SP2" = "red")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = SP1, color = "SP1")) +
  geom_line(aes(x = day, y = SP2, color = "SP2"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("SP1","SP2"))
#both good, need to take average
transformed_dat_klamath_df$SP <- rowMeans(transformed_dat_klamath_df[,c('SP1', 'SP2')], na.rm=TRUE)

color <- c("SP1" = "blue", "SP2" = "red", SP = "black")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = SP1, color = "SP1")) +
  geom_line(aes(x = day, y = SP2, color = "SP2"))+
  geom_line(aes(x = day, y = SP, color = "SP"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("SP1","SP2", "SP"))

```

```{r}
#FG
color <- c("FG2" = "blue", "FG3" = "red")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = FG2, color = "FG2")) +
  geom_line(aes(x = day, y = FG3, color = "FG3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("FG2","FG3"))
#need to remove FG2
```

```{r}
#GP
color <- c("GP1" = "blue", "GP2" = "red", "GP3" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = GP1, color = "GP1")) +
  geom_line(aes(x = day, y = GP2, color = "GP2"))+
  geom_line(aes(x = day, y = GP3, color = "GP3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("GP1","GP2","GP3"))
#need to remove GP1
transformed_dat_klamath_df$GP <- rowMeans(transformed_dat_klamath_df[,c('GP2', 'GP3')], na.rm=TRUE)

color <- c("GP" = "black", "GP2" = "red", "GP3" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = GP, color = "GP")) +
  geom_line(aes(x = day, y = GP2, color = "GP2"))+
  geom_line(aes(x = day, y = GP3, color = "GP3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("GP","GP2","GP3"))

```

```{r}
#UL
color <- c("ULout" = "blue", "UL1" = "red", "UL3" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = ULout, color = "ULout")) +
  geom_line(aes(x = day, y = UL1, color = "UL1"))+
  geom_line(aes(x = day, y = UL3, color = "UL3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("ULout","UL1","UL3"))
#need to remove UL1
transformed_dat_klamath_df$UL <- rowMeans(transformed_dat_klamath_df[,c('ULout', 'UL3')], na.rm=TRUE)

color <- c("ULout" = "blue", "UL" = "black", "UL3" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = ULout, color = "ULout")) +
  geom_line(aes(x = day, y = UL, color = "UL"))+
  geom_line(aes(x = day, y = UL3, color = "UL3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("ULout","UL","UL3"))

```

```{r}
#LL
color <- c("LL1" = "blue", "LL2" = "red", "LL3" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = LL1, color = "LL1")) +
  geom_line(aes(x = day, y = LL2, color = "LL2"))+
  geom_line(aes(x = day, y = LL3, color = "LL3"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("LL1","LL2","LL3"))
#all ok
transformed_dat_klamath_df$LL <- rowMeans(transformed_dat_klamath_df[,c('LL1','LL2', 'LL3')], na.rm=TRUE)

color <- c("LL1" = "blue", "LL2" = "red", "LL3" = "green", 'LL' = "black")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = LL1, color = "LL1")) +
  geom_line(aes(x = day, y = LL2, color = "LL2"))+
  geom_line(aes(x = day, y = LL3, color = "LL3"))+
   geom_line(aes(x = day, y = LL, color = "LL"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("LL1","LL2","LL3", "LL"))
```

```{r}
#SC
color <- c("APck" = "blue", "SPck" = "red", "LSck" = "green", "MayCk"="orange")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = APck, color = "APck")) +
  geom_line(aes(x = day, y = SPck, color = "SPck"))+
  geom_line(aes(x = day, y = LSck, color = "LSck"))+
  geom_line(aes(x = day, y = MayCk, color = "MayCk"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("APck","SPck","LSck","MayCk"))
#need to remove APck and SPck
transformed_dat_klamath_df$SC <-  rowMeans(transformed_dat_klamath_df[,c('LSck','MayCk')], na.rm=TRUE)

color <- c("SC" = "black","LSck" = "green", "MayCk"="orange")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = SC, color = "SC"))+
  geom_line(aes(x = day, y = LSck, color = "LSck"))+
  geom_line(aes(x = day, y = MayCk, color = "MayCk"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("SC","LSck","MayCk"))
```

```{r}
#HC
color <- c("FGck" = "blue", "GPck" = "red", "ULck" = "green")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = FGck, color = "FGck")) +
  geom_line(aes(x = day, y = GPck, color = "GPck"))+
  geom_line(aes(x = day, y = ULck, color = "ULck"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("FGck","GPck","ULck"))
#need to remove GPck
transformed_dat_klamath_df$HC <- rowMeans(transformed_dat_klamath_df[,c('ULck','FGck')], na.rm=TRUE)

color <- c("FGck" = "blue", "ULck" = "green", "HC" = "black")
transformed_dat_klamath_df %>% rowid_to_column(var = "day") %>% ggplot()+
  geom_line(aes(x = day, y = FGck, color = "FGck")) +
  geom_line(aes(x = day, y = ULck, color = "ULck"))+
   geom_line(aes(x = day, y = HC, color = "HC"))+
  labs(x = "day", y = "site", color = "Legend")+
  theme_classic()+
  scale_color_manual(values = color, labels = c("FGck","ULck", "HC"))
```
#Matrix of transformed data with 12 sites (condensed_transdat)
```{r}
condensed_transdat_df <- cbind(AP = transformed_dat_klamath_df$AP3, SP = transformed_dat_klamath_df$SP, Durazo = transformed_dat_klamath_df$Durazo, LS = transformed_dat_klamath_df$LS, May = transformed_dat_klamath_df$May, FG = transformed_dat_klamath_df$FG3, GP = transformed_dat_klamath_df$GP, UL = transformed_dat_klamath_df$UL, LL = transformed_dat_klamath_df$LL, SC = transformed_dat_klamath_df$SC, HC = transformed_dat_klamath_df$HC, KSV = transformed_dat_klamath_df$KSV)
condensed_transdat <- as.matrix(t(condensed_transdat_df))
str(condensed_transdat)

saveRDS(condensed_transdat, "condensed_transdat.rds")
```


# Hypothesis 1: all states have different levels of stochastic (Q) and deterministic (C) variability 
## AICc -9599.906
```{r}
mod1_condense = list()
mod1_condense$A = "zero" 
mod1_condense$Z = "identity"
mod1_condense$R = "zero" #all the sensors are same, so observation error should be same
mod1_condense$Q = "diagonal and unequal" 
mod1_condense$B = "diagonal and unequal" #assuming no species interactions
mod1_condense$U = "zero"  
mod1_condense$C = "unequal" 
mod1_condense$c = transformed_covariate_klamath
mod1_condense.fit = MARSS(condensed_transdat, model=mod1_condense)
mod1_condense.params =MARSSparamCIs(mod1_condense.fit)
MARSSparamCIs(mod1_condense.fit)
```

```{r}
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod1_condense.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

# Hypothesis 2: all states have save levels of stochastic (Q) and deterministic (C) variability
## AICc -8356.184  
```{r}
mod2_condense = list()
mod2_condense$A = "zero" 
mod2_condense$Z = "identity"
mod2_condense$R = "zero" #all the sensors are same, so observation error should be same
mod2_condense$Q = "diagonal and equal" 
mod2_condense$B = "diagonal and equal" #assuming no species interactions
mod2_condense$U = "zero"  
mod2_condense$C = "equal" 
mod2_condense$c = transformed_covariate_klamath
mod2_condense.fit = MARSS(condensed_transdat, model=mod2_condense)
mod2_condense.params =MARSSparamCIs(mod2_condense.fit)
MARSSparamCIs(mod2_condense.fit)
```
```{r}
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod2_condense.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

# Hypothesis 3: Habitat type: Creeks vs ponds vs Klamath
## AICc: -8586.263   
```{r}
mod3_condense = list()
## Modify matrices
# 1st: group time series into categories
hypothesis = c("pond","pond","pond","pond",
               "pond","pond","pond","pond",
               "pond","creek","creek","Klamath")

# 2nd: build C matrix (12 x 1)
mod3_condense$C = matrix(hypothesis)
mod3_condense$c = transformed_covariate_klamath

# 3rd: build Q matrix (12 x 12, with "C vector" in its diagonal)
Q <-  matrix(list("pond",0,0,0,0,0,0,0,0,0,0,0,
                  0,"pond",0,0,0,0,0,0,0,0,0,0,
                  0,0,"pond",0,0,0,0,0,0,0,0,0,
                  0,0,0,"pond",0,0,0,0,0,0,0,0,
                  0,0,0,0,"pond",0,0,0,0,0,0,0,
                  0,0,0,0,0,"pond",0,0,0,0,0,0,
                  0,0,0,0,0,0,"pond",0,0,0,0,0,
                  0,0,0,0,0,0,0,"pond",0,0,0,0,
                  0,0,0,0,0,0,0,0,"pond",0,0,0,
                  0,0,0,0,0,0,0,0,0,"creek",0,0,
                  0,0,0,0,0,0,0,0,0,0,"creek",0,
                  0,0,0,0,0,0,0,0,0,0,0,"Klamath"),12,12)

# 4th: B, identical as Q
B <- Q

mod3_condense$A = "zero" 
mod3_condense$Z = "identity"
mod3_condense$R = "zero" #all the sensors are same, so observation error should be same
mod3_condense$Q = Q 
mod3_condense$B = Q
mod3_condense$U = "zero"  
mod3_condense$C = matrix(hypothesis) 
mod3_condense$c = transformed_covariate_klamath
mod3_condense.fit = MARSS(condensed_transdat, model=mod3_condense)
mod3_condense.params =MARSSparamCIs(mod3_condense.fit)
MARSSparamCIs(mod3_condense.fit)

```
```{r}
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod3_condense.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```
# Hypothesis 4: By watershed
## AICc:   -8597.364  
```{r}
mod4_condense = list()
## Modify matrices
# 1st: group time series into categories
rownames(condensed_transdat)
hypothesis2 = c("SC","SC","SC","SC",
               "SC","HC","HC","HC",
               "HC","SC","HC","Klamath")

# 2nd: build C matrix (12 x 1)
mod4_condense$C = matrix(hypothesis2)
mod4_condense$c = transformed_covariate_klamath

# 3rd: build Q matrix (12 x 12, with "C vector" in its diagonal)
Q <-  matrix(list("SC",0,0,0,0,0,0,0,0,0,0,0,
                  0,"SC",0,0,0,0,0,0,0,0,0,0,
                  0,0,"SC",0,0,0,0,0,0,0,0,0,
                  0,0,0,"SC",0,0,0,0,0,0,0,0,
                  0,0,0,0,"SC",0,0,0,0,0,0,0,
                  0,0,0,0,0,"HC",0,0,0,0,0,0,
                  0,0,0,0,0,0,"HC",0,0,0,0,0,
                  0,0,0,0,0,0,0,"HC",0,0,0,0,
                  0,0,0,0,0,0,0,0,"HC",0,0,0,
                  0,0,0,0,0,0,0,0,0,"SC",0,0,
                  0,0,0,0,0,0,0,0,0,0,"HC",0,
                  0,0,0,0,0,0,0,0,0,0,0,"Klamath"),12,12)

# 4th: B, identical as Q
B <- Q

mod4_condense$A = "zero" 
mod4_condense$Z = "identity"
mod4_condense$R = "zero" #all the sensors are same, so observation error should be same
mod4_condense$Q = Q 
mod4_condense$B = Q
mod4_condense$U = "zero"  
mod4_condense$C = matrix(hypothesis2) 
mod4_condense$c = transformed_covariate_klamath
mod4_condense.fit = MARSS(condensed_transdat, model=mod4_condense)
mod4_condense.params =MARSSparamCIs(mod4_condense.fit)
MARSSparamCIs(mod4_condense.fit)

```

#Plot Covariates
```{r}
mod1_condense.fit = MARSS(condensed_transdat, model=mod1_condense)
mod1_condense.params =MARSSparamCIs(mod1_condense.fit)
MARSSparamCIs(mod1_condense.fit)


mod1_condense.params
mod1_condense_df <- broom::tidy(mod1_condense.fit)

png("Fig_AirTempEffects.png", width = 700, height = 400)
labels <- c("Alexander", "Durazo", "FishGulch", "Goodman","HorseCreek","Klamath","LLawrence","LowerSeiad","May","SeiadCreek","Stender","ULawrence")
ggplot(data = mod1_condense_df) + 
  geom_pointrange(data = mod1_condense_df[c(37:48),], aes(x = term, y = estimate, ymin = conf.low, ymax = conf.up), color = "black") +
  geom_hline(yintercept = 0) +
  labs(x = "Sites",
       y = "Air Temperature Effects") +
  ggtitle("Air Temperature Effects") +
  theme_classic()+
  theme(text=element_text(size=20),axis.text.x=element_text(angle = 90, hjust = 1))+
  scale_x_discrete(labels= labels)
dev.off()
```
```{r}
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod4_condense.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```
