---
title: "MARSS model checking"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(patchwork)
library(astsa)
library(forecast)
library(dplyr)
library(pander)
library(MARSS)
library(MASS)
library(gridExtra)
library(weathermetrics)
```



##################################################################################
##2020 MARSS model outputs
###July 7 - July 28 2020 (airtemp as a covariate, but not z scored. No seasonal correction)
```{r}
mod1.fit.2020 <- readRDS("2020_mod1.fit.rds")
mod1.params.2020 <- readRDS("2020_mod1.params.rds")
mod2.fit.2020 <- readRDS("2020_mod2.fit.rds")
mod2.params.2020 <- readRDS("2020_mod2.params.rds")
mod3.fit.2020 <- readRDS("2020_mod3.fit.rds")
mod3.params.2020 <- readRDS("2020_mod3.params.rds")
mod4.fit.2020 <- readRDS("2020_mod4.fit.rds")
mod4.params.2020 <- readRDS("2020_mod4.params.rds")

#Model 1, hypothesis 1 (all separate)
mod1.params.2020 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod1.fit.2020, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 2, hypothesis 2 (creeks vs ponds)
mod2.params.2020 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod2.fit.2020, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 3, hypothesis 3 (trib vs. trib)
mod3.params.2020
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod3.fit.2020, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 4, hypothesis 4 (all same)
mod4.params.2020
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod4.fit.2020, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#...these models are actually okay, but short
```
###AICc 2020
```{r}
data.frame(Model=c("Model1", "Model2", "Model3", "Model4"),
           AICc=round(c(mod1.fit.2020$AICc,
                        mod2.fit.2020$AICc,
                        mod3.fit.2020$AICc,
                        mod4.fit.2020$AICc),1))
```

##################################################################################
##2021 MARSS models 
###Covariates (not z scored) and Mean temps (z scored, log transformed)
```{r, include = F}
#Original data matrix creation: Daily temperature averages (mean) 
matrix7 <- matrix(nrow=26,ncol=378)
matrix7[1,] <- AP1_daily$mean_temp
matrix7[2,] <- AP2_daily$mean_temp
matrix7[3,] <- AP3_daily$mean_temp
matrix7[4,] <- APck_daily$mean_temp
matrix7[5,] <- SP1_daily$mean_temp
matrix7[6,] <- SP2_daily$mean_temp
matrix7[7,] <- SPck_daily$mean_temp
matrix7[8,] <- Durazo_daily$mean_temp
matrix7[9,] <- LS_daily$mean_temp
matrix7[10,] <- LSck_daily$mean_temp
matrix7[11,] <- May_daily$mean_temp
matrix7[12,] <- MayCk_daily$mean_temp
matrix7[13,] <- FG2_daily$mean_temp
matrix7[14,] <- FG3_daily$mean_temp
matrix7[15,] <- FGck_daily$mean_temp
matrix7[16,] <- GP1_daily$mean_temp
matrix7[17,] <- GP2_daily$mean_temp
matrix7[18,] <- GP3_daily$mean_temp
matrix7[19,] <- GPck_daily$mean_temp
matrix7[20,] <- ULout_daily$mean_temp
matrix7[21,] <- UL1_daily$mean_temp
matrix7[22,] <- UL3_daily$mean_temp
matrix7[23,] <- ULck_daily$mean_temp
matrix7[24,] <- LL1_daily$mean_temp
matrix7[25,] <- LL2_daily$mean_temp
matrix7[26,] <- LL3_daily$mean_temp

#log transform and de-mean the data
transformed_dat_0 <- zscore(matrix7)
transformed_dat_0 <- log(transformed_dat_0)
saveRDS(transformed_dat_0,"transformed_dat_0.rds")

```

```{r, include = F}
matrix2 <- readRDS("matrix2.rds")
matrix3 <- readRDS("matrix3.rds")
matrix4 <- readRDS("matrix4.rds")
matrix5 <- readRDS("matrix5.rds")
airtemp <- readRDS("airtemp.rds") #raw data
```

```{r}
#Build the little c matrix, call it matrixc_0
matrixc_0 <- matrix(nrow=1,ncol=378)
matrixc_0 <- t(as.matrix(airtemp$TAVG))
saveRDS(matrixc_0,"matrixc_0.rds")
str(matrixc_0)

```

###MARSS models
```{r }
#Hypothesis 1, Model 1: All ponds and creeks are separate
mod1 = list()
mod1$A = "zero" #no trend because we z scored
mod1$Z = matrix2
mod1$R = "diagonal and equal" #all the sensors are the same type, so observation error should be the same
mod1$Q = "unconstrained" #leave Q unconstrained because we expect some covariance between sensors (also try Equalvarcov)
mod1$B = "identity" #assuming no species interactions
mod1$U = "zero" #no trend because we z scored 
mod1$C = "unequal" #I think I can set C to unequal because it is going off the Z matrix where I have already indicated how to split up the sites.
mod1$c = matrixc_0
mod1.fit = MARSS(transformed_dat_0, model=mod1, control=list(maxit=10000))
mod1.params = MARSSparamCIs(mod1.fit)
saveRDS(mod1.fit,"mod1.fit.rds")
saveRDS(mod1.params,"mod1.params.rds")

#Hypothesis 2, Model 3: ponds vs. creeks 
mod2 <- mod1 
mod2$Z <- matrix3
mod2.fit = MARSS(transformed_dat_0, model=mod2, control=list(maxit=10000))
mod2.params = MARSSparamCIs(mod2.fit)
saveRDS(mod2.fit,"mod2.fit.rds")
saveRDS(mod2.params,"mod2.params.rds")

#Hypothesis 3, Model 3: Tributary versus tributary
mod3 <- mod1
mod3$Z = matrix4
mod3.fit = MARSS(transformed_dat_0, model=mod3, control=list(maxit=10000))
mod3.params = MARSSparamCIs(mod3.fit)
saveRDS(mod3.fit,"mod3.fit.rds")
saveRDS(mod3.params,"mod3.params.rds")

#Hypothesis 4, Model 4: All same
mod4 <- mod1 
mod4$Z <- matrix5
mod4.fit = MARSS(transformed_dat_0, model=mod4, control=list(maxit=10000))
mod4.params =MARSSparamCIs(mod4.fit)
saveRDS(mod4.fit,"mod4.fit.rds")
saveRDS(mod4.params,"mod4.params.rds")
```

###Residuals
```{r}
mod1.fit <- readRDS("mod1.fit.rds")
mod1.params <- readRDS("mod1.params.rds")
mod2.fit <- readRDS("mod2.fit.rds")
mod2.params <- readRDS("mod2.params.rds")
mod3.fit <- readRDS("mod3.fit.rds")
mod3.params <- readRDS("mod3.params.rds")
mod4.fit <- readRDS("mod4.fit.rds")
mod4.params <- readRDS("mod4.params.rds")

#Model 1, hypothesis 1 (all separate)
mod1.params 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod1.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 2, hypothesis 2 (creeks vs ponds)
mod2.params 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod2.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 3, hypothesis 3 (trib vs. trib)
mod3.params
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod3.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 4, hypothesis 4 (all same)
mod4.params
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod4.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#...these models are not good
```

###AICc 2021
```{r}
data.frame(Model=c("Model1", "Model2", "Model3", "Model4"),
           AICc=round(c(mod1.fit$AICc,
                        mod2.fit$AICc,
                        mod3.fit$AICc,
                        mod4.fit$AICc),1))
```

###############################################################################################
##2021 FT MARSS
###correct for seasonality using Fourier Series, and z-scoring airtemperature as an additional covariate
```{r}
#Correct for seasonality using Fourier Series
TT = ncol(transformed_dat) # number of time periods/samples
period = 365 # number of "seasons" (e.g., 12 months per year)
per.1st = 1 # first "season" (e.g., Jan = 1, July = 7)
c = diag(period) # create factors for seasons
for(i in 2:(ceiling(TT/period))) {c = cbind(c,diag(period))}
dim(c)

#Create Fourier Series
cos.t = cos(2 * pi * seq(TT) / period)
sin.t = sin(2 * pi * seq(TT) / period)
c.Four = rbind(cos.t,sin.t)
cor(c.Four[1,],c.Four[2,]) # not correlated!
matplot(t(c.Four), type="l")

#Now fit model with seasonality AND an additional covariate (airtemp from above)
airtemp_z <- zscore(airtemp$TAVG) 
newcovarsFour_airtemp <-rbind(c.Four, "airtemp"=airtemp_z)
matplot(t(newcovarsFour_airtemp), type="l", col=c("black","red","blue"))
```
###MARSS models
```{r }
#Hypothesis 1, Model 5: All ponds and creeks are separate
mod5 = list()
mod5$A = "zero" #no trend because we z scored
mod5$Z = matrix2
mod5$R = "diagonal and equal" #all the sensors are the same type, so observation error should be the same
mod5$Q = "unconstrained" #leave Q unconstrained because we expect some covariance between sensors (also try Equalvarcov)
mod5$B = "identity" #assuming no species interactions
mod5$U = "zero" #no trend because we z scored 
mod5$C = "unequal" #I think I can set C to unequal because it is going off the Z matrix where I have already indicated how to split up the sites.
mod5$c = newcovarsFour_airtemp
mod5.fit = MARSS(transformed_dat_0, model=mod5, control=list(maxit=10000))
mod5.params = MARSSparamCIs(mod5.fit)
saveRDS(mod5.fit,"mod5.fit.rds")
saveRDS(mod5.params,"mod5.params.rds")

#Hypothesis 2, Model 3: ponds vs. creeks 
mod6 <- mod5 
mod6$Z <- matrix3
mod6.fit = MARSS(transformed_dat_0, model=mod6, control=list(maxit=10000))
mod6.params = MARSSparamCIs(mod6.fit)
saveRDS(mod6.fit,"mod6.fit.rds")
saveRDS(mod6.params,"mod6.params.rds")

#Hypothesis 3, Model 3: Tributary versus tributary
mod7 <- mod5
mod7$Z = matrix4
mod7.fit = MARSS(transformed_dat_0, model=mod7, control=list(maxit=10000))
mod7.params = MARSSparamCIs(mod7.fit)
saveRDS(mod7.fit,"mod7.fit.rds")
saveRDS(mod7.params,"mod7.params.rds")

#Hypothesis 4, Model 4: All same
mod8 <- mod5 
mod8$Z <- matrix5
mod8.fit = MARSS(transformed_dat_0, model=mod8, control=list(maxit=10000))
mod8.params =MARSSparamCIs(mod8.fit)
saveRDS(mod8.fit,"mod8.fit.rds")
saveRDS(mod8.params,"mod8.params.rds")

```

###Residuals
```{r }
mod5.fit <- readRDS("mod5.fit.rds")
mod5.params <- readRDS("mod5.params.rds")
mod6.fit <- readRDS("mod6.fit.rds")
mod6.params <- readRDS("mod6.params.rds")
mod7.fit <- readRDS("mod7.fit.rds")
mod7.params <- readRDS("mod7.params.rds")
mod8.fit <- readRDS("mod8.fit.rds")
mod8.params <- readRDS("mod8.params.rds")

#Model 5, hypothesis 1 (all separate)
mod5.params 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod5.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 6, hypothesis 2 (creeks vs ponds)
mod6.params 
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod6.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 7, hypothesis 3 (trib vs. trib)
mod7.params
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod7.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#Model 8, hypothesis 4 (all same)
mod8.params
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod8.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }

#...these models are not good
```

###AICc FT
```{r }
data.frame(Model=c("Model5", "Model6", "Model7", "Model8"),
           AICc=round(c(mod5.fit$AICc,
                        mod6.fit$AICc,
                        mod7.fit$AICc,
                        mod8.fit$AICc),1))

```

###############################################################################################
##Fixing transformations
###Re-run models by NOT log transforming the data, z scoring covariates, and changing Q to diagonal and unequal, NO FT needed

###Data (Z scored only)
Recall: rows are states, columns are time steps. 
```{r, include = F}
matrix7 <- readRDS("matrix7.rds")
#z score the data
transformed_dat_1 <- zscore(matrix7)
saveRDS(transformed_dat_1,"transformed_dat_1.rds") #NO log transformation here
```

###Covariates (z scored only)
```{r, include=FALSE}
airtemp_1 <- zscore(airtemp$TAVG)
#Build the little c matrix, call it matrixc_1
matrixc_1 <- matrix(nrow=1,ncol=378)
matrixc_1 <- t(as.matrix(airtemp_1))
matrixc_1 <- zscore(matrixc_1)
saveRDS(matrixc_1,"matrixc_1.rds")

```
###MARSS models
```{r}
#Test on Hypothesis 3 (easy to run)
mod9 = list()
mod9$A = "zero" #no trend because we z scored
mod9$Z = matrix4
mod9$R = "diagonal and equal" #all the sensors are the same type, so observation error should be the same
mod9$Q = "diagonal and unequal" #(also try Equalvarcov)
mod9$B = "identity" #assuming no species interactions
mod9$U = "zero" #no trend because we z scored 
mod9$C = "unequal" #I think I can set C to unequal because it is going off the Z matrix where I have already indicated how to split up the sites.
mod9$c = matrixc_1
mod9.fit = MARSS(transformed_dat_1, model=mod9, control=list(maxit=10000))
mod9.params = MARSSparamCIs(mod9.fit)
saveRDS(mod9.fit,"mod9.fit.rds")
saveRDS(mod9.params,"mod9.params.rds")

par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod9.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

###############################################################################################
##Removing odd data
###Re-run model 9 by removing AP3 (short dataset)

###Data (Z scored only)
Recall: rows are states, columns are time steps. 
```{r, include = F}
matrix7 <- readRDS("matrix7.rds")
#z score the data
transformed_dat_2 <- zscore(matrix7)
saveRDS(transformed_dat_2,"transformed_dat_2.rds") #NO log transformation here
matplot(t(transformed_dat_2))

########Need to remove AP2 as an outlier########
transformed_dat_2 <- transformed_dat_2[-2,]
```

###Re-do Z-Matrices
```{r }
matrix2 <- readRDS("matrix2.rds")
matrix3 <- readRDS("matrix3.rds")
matrix4 <- readRDS("matrix4.rds")
matrix5 <- readRDS("matrix5.rds")

matrix2 <- matrix2[-2,]
matrix3 <- matrix3[-2,]
matrix4 <- matrix4[-2,]
matrix5 <- matrix5[-2,]
dim(matrix4)
```

###Covariates (z scored only)
```{r, include=FALSE}
airtemp <- zscore(airtemp$TAVG)
#Build the little c matrix, call it matrixc_2
matrixc_2 <- matrix(nrow=1,ncol=378)
matrixc_2 <- t(as.matrix(airtemp))
matrixc_2 <- zscore(matrixc_2)
saveRDS(matrixc_2,"matrixc_2.rds")

```
###MARSS models
```{r}
#Test on Hypothesis 3 (easy to run)
mod10 = list()
mod10$A = "zero" #no trend because we z scored
mod10$Z = matrix4
mod10$R = "diagonal and equal" #all the sensors are the same type, so observation error should be the same
mod10$Q = "diagonal and unequal" #(also try Equalvarcov)
mod10$B = "identity" #assuming no species interactions
mod10$U = "zero" #no trend because we z scored 
mod10$C = "unequal" #I think I can set C to unequal because it is going off the Z matrix where I have already indicated how to split up the sites.
mod10$c = matrixc_1
mod10.fit = MARSS(transformed_dat_1, model=mod10, control=list(maxit=10000))
mod10.params = MARSSparamCIs(mod10.fit)
saveRDS(mod10.fit,"mod10.fit.rds")
saveRDS(mod10.params,"mod10.params.rds")

par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod10.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```
##^That's the one!Albert double checked model 10 and thinks it's good. 